Learning CNN filters from user-drawn image \changed{markers} for coconut-tree image classification

### 2020-08-10 text.tex
changing project structure

%!TEX root = main.tex

@@

\begin{figure}[!ht]
  \centering
  \subfloat[\label{fig:ex-groups}]
  {\includegraphics[width=.35\linewidth]{figures/example_groups/groups_centered}}
  ~
  \subfloat[\label{fig:ex-groups-after}]{\includegraphics[width=.45\linewidth]{figures/example_groups/groups3d_centered}
  }
  \caption{(a) A 2D feature space with color-coded samples from two classes distributed in three groups. (b) After marker-based batch normalization and convolution with filters obtained from each group, the classes can be more easily detected by two filters in a new 3D feature space.}
  \label{fig:filter}
\end{figure}

@@

    \begin{tikzpicture}
    %images----------------------------
     \node (img1) [image] {\includegraphics[width=.08\textwidth]{figures/qualitative/ours/lower-coco-789.png}};
     \node (img2) [image, below left=-5em of img1] {\includegraphics[width=.08\textwidth]{figures/qualitative/ours/lower-non_coco-105.png}};
     \node (img3) [image, below left=-5em of img2] {\includegraphics[width=.08\textwidth]{figures/qualitative/vgg/lower-coco-2212.png}};
     \node (img4) [image, below left=-5em of img3] {\includegraphics[width=.08\textwidth]{figures/qualitative/ours/upper-coco-108.png}};

@@

     \node (vis1) [image, right=1.5em of tsne, outer sep=0pt, label = {[label distance = 0.1em]below:{Projection}}] {\includegraphics[width=.12\textwidth]{figures/input_200.png}};

@@

    %images----------------------------
    \node (simg1) [image, above right=-2.5em and 3.4em of select] {\includegraphics[width=.08\textwidth]{figures/img4.png}};
    \node (simg2) [image, below left=-5em of simg1] {\includegraphics[width=.08\textwidth]{figures/img2.png}};
    \node (simg3) [image, below left=-5em of simg2] {\includegraphics[width=.08\textwidth]{figures/img3.png}};
    \node (simg4) [image, below left=-5em of simg3] {\includegraphics[width=.08\textwidth]{figures/img1.png}};

@@

     %images----------------------------
    \node (mimg1) [image, above right=-2.5em and 3.4em of put] {\includegraphics[width=.08\textwidth]{figures/markers4.png}};
    \node (mimg2) [image, below left=-5em of mimg1] {\includegraphics[width=.08\textwidth]{figures/markers2.png}};
    \node (mimg3) [image, below left=-5em of mimg2] {\includegraphics[width=.08\textwidth]{figures/markers3.png}};
    \node (mimg4) [image, below left=-5em of mimg3] {\includegraphics[width=.08\textwidth]{figures/markers1.png}};

@@

    \node (user) [image, below=1.9em of simgs, outer sep = -.5em, label = {[label distance = 0.3em]below:{User}}] {\includegraphics[width=.07\textwidth]{figures/user.png}};

@@

\begin{figure}[!t]
    \centering
    \subfloat[\label{fig:markers1}]{\includegraphics[width=.25\linewidth]{figures/markers1}
    }
    ~
    \subfloat[\label{fig:markers2}]{\includegraphics[width=.25\linewidth]{figures/markers2}
    }
    \\
    \subfloat[\label{fig:markers3}]{\includegraphics[width=.25\linewidth]{figures/markers3}
    }
    ~
    \subfloat[\label{fig:markers4}]{\includegraphics[width=.25\linewidth]{figures/markers4}
    }
    \caption{\changed{Markers used for training, cyan markers on coconut-tree pixels and orange markers on background pixels.}}
    \label{fig:markers}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat{\includegraphics[width=.2\linewidth]{figures/qualitative/ours/upper-coco-108.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figures/qualitative/ours/upper-coco-2473.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figures/qualitative/ours/upper-non_coco-506.png}
  }
  \\
  \subfloat{\includegraphics[width=.2\linewidth]{figures/qualitative/vgg/lower-coco-1098.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figures/qualitative/vgg/lower-coco-875.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figures/qualitative/vgg/lower-non_coco-105.png}
  }
  \caption{Misclassified images by ``FLIM + MLP'' (first row) and VGG-FT (second row), being the last column with images without coconut trees.}
  \label{fig:ex-classification}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[\label{fig:vis-input}]{\includegraphics[width=.3\linewidth]{figures/input}
  }
  ~
  \subfloat[\label{fig:vis-feature-extractor}]{\includegraphics[width=.3\linewidth]{figures/feature_extractor}
  }
  ~
  \subfloat[]{\includegraphics[width=.3\linewidth]{figures/classifier}
  \label{fig:vis-classifier}}
  \caption{Projections by t-SNE of the test images at (a) the input layer, (b) the output of the convolutional layer of  FLIM+MLP after batch normalization (Figure~\ref{fig:arch}), and (c) the output of the last hidden layer of the MLP classifier in  FLIM+MLP.}
\end{figure}

@@

This research was funded by FAPESP (2014/12236-1), CNPq (303808/2018-7), Petróleo Brasileiro S.A. (PETROBRAS) and Agência Nacional do Petróleo, Gás Natural e Biocombustíveis (ANP), Grant Numbers 4600556376 and 4600583791.
\bibliographystyle{IEEEtran}
\bibliography{bibliography}

>>>>

%!TEX root = arxiv.tex

@@

\begin{figure}[!ht]
  \centering
  \subfloat[\label{fig:ex-groups}]
  {\includegraphics[width=.35\linewidth]{figs/example_groups/groups_centered}}
  ~
  \subfloat[\label{fig:ex-groups-after}]{\includegraphics[width=.45\linewidth]{figs/example_groups/groups3d_centered}
  }
  \caption{(a) A 2D feature space with color-coded samples from two classes distributed in three groups. (b) After marker-based batch normalization and convolution with filters obtained from each group, the classes can be more easily detected by two filters in a new 3D feature space.}
  \label{fig:filter}
\end{figure}

@@

    \begin{tikzpicture}
    %images----------------------------
     \node (img1) [image] {\includegraphics[width=.08\textwidth]{figs/qualitative/ours/lower-coco-789.png}};
     \node (img2) [image, below left=-5em of img1] {\includegraphics[width=.08\textwidth]{figs/qualitative/ours/lower-non_coco-105.png}};
     \node (img3) [image, below left=-5em of img2] {\includegraphics[width=.08\textwidth]{figs/qualitative/vgg/lower-coco-2212.png}};
     \node (img4) [image, below left=-5em of img3] {\includegraphics[width=.08\textwidth]{figs/qualitative/ours/upper-coco-108.png}};

@@

     \node (vis1) [image, right=1.5em of tsne, outer sep=0pt, label = {[label distance = 0.1em]below:{Projection}}] {\includegraphics[width=.12\textwidth]{figs/input_200.png}};

@@

    %images----------------------------
    \node (simg1) [image, above right=-2.5em and 3.4em of select] {\includegraphics[width=.08\textwidth]{figs/img4.png}};
    \node (simg2) [image, below left=-5em of simg1] {\includegraphics[width=.08\textwidth]{figs/img2.png}};
    \node (simg3) [image, below left=-5em of simg2] {\includegraphics[width=.08\textwidth]{figs/img3.png}};
    \node (simg4) [image, below left=-5em of simg3] {\includegraphics[width=.08\textwidth]{figs/img1.png}};

@@

     %images----------------------------
    \node (mimg1) [image, above right=-2.5em and 3.4em of put] {\includegraphics[width=.08\textwidth]{figs/markers4.png}};
    \node (mimg2) [image, below left=-5em of mimg1] {\includegraphics[width=.08\textwidth]{figs/markers2.png}};
    \node (mimg3) [image, below left=-5em of mimg2] {\includegraphics[width=.08\textwidth]{figs/markers3.png}};
    \node (mimg4) [image, below left=-5em of mimg3] {\includegraphics[width=.08\textwidth]{figs/markers1.png}};

@@

    \node (user) [image, below=1.9em of simgs, outer sep = -.5em, label = {[label distance = 0.3em]below:{User}}] {\includegraphics[width=.07\textwidth]{figs/user.png}};

@@

\begin{figure}[!t]
    \centering
    \subfloat[\label{fig:markers1}]{\includegraphics[width=.25\linewidth]{figs/markers1}
    }
    ~
    \subfloat[\label{fig:markers2}]{\includegraphics[width=.25\linewidth]{figs/markers2}
    }
    \\
    \subfloat[\label{fig:markers3}]{\includegraphics[width=.25\linewidth]{figs/markers3}
    }
    ~
    \subfloat[\label{fig:markers4}]{\includegraphics[width=.25\linewidth]{figs/markers4}
    }
    \caption{\changed{Markers used for training, cyan markers on coconut-tree pixels and orange markers on background pixels.}}
    \label{fig:markers}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat{\includegraphics[width=.2\linewidth]{figs/qualitative/ours/upper-coco-108.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figs/qualitative/ours/upper-coco-2473.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figs/qualitative/ours/upper-non_coco-506.png}
  }
  \\
  \subfloat{\includegraphics[width=.2\linewidth]{figs/qualitative/vgg/lower-coco-1098.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figs/qualitative/vgg/lower-coco-875.png}
  }
  ~
  \subfloat{\includegraphics[width=.2\linewidth]{figs/qualitative/vgg/lower-non_coco-105.png}
  }
  \caption{Misclassified images by ``FLIM + MLP'' (first row) and VGG-FT (second row), being the last column with images without coconut trees.}
  \label{fig:ex-classification}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[\label{fig:vis-input}]{\includegraphics[width=.3\linewidth]{figs/input}
  }
  ~
  \subfloat[\label{fig:vis-feature-extractor}]{\includegraphics[width=.3\linewidth]{figs/feature_extractor}
  }
  ~
  \subfloat[]{\includegraphics[width=.3\linewidth]{figs/classifier}
  \label{fig:vis-classifier}}
  \caption{Projections by t-SNE of the test images at (a) the input layer, (b) the output of the convolutional layer of  FLIM+MLP after batch normalization (Figure~\ref{fig:arch}), and (c) the output of the last hidden layer of the MLP classifier in  FLIM+MLP.}
\end{figure}

@@

This research was funded by FAPESP (2014/12236-1), CNPq (303808/2018-7), Petróleo Brasileiro S.A. (PETROBRAS) and Agência Nacional do Petróleo, Gás Natural e Biocombustíveis (ANP), Grant Numbers 4600556376 and 4600583791.
\bibliographystyle{IEEEtran}
\bibliography{refs}
